Confluence in Lens Synthesis

### 2020-04-07 papers/BijectiveLenses/IWC/main.tex
add more info

Bidirectional transformations are pervasive in modern software systems, occuring
as database views and view updaters, parsers and pretty-printers, data
synchronization tools, and more. Instead of manually building the functions that
comprise a bidirectional transformation, programmers can build them both ``at
once'' using a bidirectional programming language. Bidirectional programming
languages have been developed for creating view updaters~\cite{?}, Linux
configuration file editors~\cite{?}, direct manipulation programming
systems~\cite{?}, and more~\cite{?,?,?}. Lenses are a particularly well-behaved
class of bidirectional programs, where the underlying transformations are
guaranteed to satisfy a number of ``round-tripping'' laws. Lens-based
bidirectional programming languages often provide round-tripping guarantees
through a set of typing rules; well-typed lens expressions are guaranteed to
satisfy the round-tripping laws.

To make bidirectional programming easier, Optician~\cite{?,?,?} synthesizes
bidirectional programs from these types, specifically in Boomerang, a language
for synchronizing string data. Optician takes as input two regular expressions
(which serve as the type of a Boomerang lens) and a set of examples specifying
input-output behavior, and synthesizes a well-typed lens between the languages
of those regular expressions.

@@

\label{sect:bib}
\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{local}

>>>>

Bidirectional transformations are pervasive in modern software systems, occuring
as database views and view updaters, parsers and pretty-printers, data
synchronization tools, and more. Instead of manually building the functions that
comprise a bidirectional transformation, programmers can build them both ``at
once'' using a bidirectional programming language. Bidirectional programming
languages have been developed for creating view
updaters~\cite{BohannonPierceVaughan}, Linux configuration file
editors~\cite{augeas2}, direct manipulation programming
systems~\cite{bidirectionaleval}, and
more~\cite{DBLP:conf/pepm/KoZH16,DBLP:conf/icfp/HidakaHIKMN10,DBLP:conf/staf/ZhuK0SH15}. Lenses are a
particularly well-behaved class of bidirectional programs, where the underlying
transformations are guaranteed to satisfy a number of ``round-tripping'' laws.
Lens-based bidirectional programming languages often provide round-tripping
guarantees through a set of typing rules; well-typed lens expressions are
guaranteed to satisfy the round-tripping laws.

To make bidirectional programming easier, Optician~\cite{optician} synthesizes
bidirectional programs from these types, specifically in Boomerang, a language
for synchronizing string data. Optician takes as input two regular expressions
(which serve as the type of a Boomerang lens) and a set of examples specifying
input-output behavior, and synthesizes a well-typed lens between the languages
of those regular expressions.

@@

\label{sect:bib}
\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{local,bcp}
